An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-17 paper/paper.tex
Fix typo in ARS caption
Update link to GitHub

For reproducibility, we make our code, data and figures publicly available at \url{https://github.com/CN-TU/adversarial-recurrent-ids}.

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{../plots/ars_original.pdf}
\caption{Recall for each attack type and \gls{ars} for CIC-IDS-2017. For ``PortScan, Firewall'' recall never falls under 66\%: The adversary does not succeed and that \gls{ars} is $\infty$.}
\label{fig:recall_ars}
\end{figure}

>>>>

We make all the source code, data and figures freely available to enable reproducibility and encourage experimentation at \url{https://github.com/CN-TU/adversarial-recurrent-ids}.

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{../plots/ars_original.pdf}
\caption{Recall for each attack type and \gls{ars} for CIC-IDS-2017. For ``PortScan, Firewall'' recall never falls under 66\%: The adversary does not succeed and the \gls{ars} is $\infty$.}
\label{fig:recall_ars}
\end{figure}
